An Analysis of Parallel Rendering Systems

### 2007-01-11 WhitePapers/ParallelRenderingSystems/paper.tex
website: update api page, update parallel rendering systems WP

We advocate the need for a generic, open parallel rendering framework to
build scalable graphics software. The inherent limitations of transparent
multi-pipe software are justified, and a full software stack for
graphics clusters is outlined.
}
\vfill
{\center\begin{tabularx}{.88\textwidth}{|l|l|X|}
\hline
\bf Version & \bf Date & \bf Changes \\
\hline
0.5.2       & September 19, 2006   & Tweaked Figure~\ref{FIG_parallel}\\
0.5.1       & July 5, 2006         & Added link to latest version\\
0.5         & May 19, 2006         & Initial Version\\
\hline
\multicolumn{3}{c}{\footnotesize Latest version at 
  \htmladdnormallink{http://www.equalizergraphics.com/documents/ParallelRenderingSystems.pdf}
  {http://www.equalizergraphics.com/documents/ParallelRenderingSystems.pdf}}\\
\end{tabularx}}
\clearpage
\pagenumbering{arabic}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\columnwidth]{images/sp_to_mp.pdf}
\caption{Some advanced display systems}
\label{FIG_parallel}
\end{figure}

>>>>

We advocate the need for a generic, open parallel rendering framework to
build scalable graphics software. The inherent limitations of transparent
multi-pipe software are justified, and a full software stack for
graphics clusters is outlined.
}
\vfill
{\center\begin{tabularx}{.88\textwidth}{|l|l|X|}
\hline
\bf Version & \bf Date & \bf Changes \\
\hline
0.5.3       & January 11, 2007     & Updated Figure~\ref{FIG_multipipe}\\
0.5.2       & September 19, 2006   & Tweaked Figure~\ref{FIG_parallel}\\
0.5.1       & July 5, 2006         & Added link to latest version\\
0.5         & May 19, 2006         & Initial Version\\
\hline
\multicolumn{3}{c}{\footnotesize Latest version at 
  \htmladdnormallink{http://www.equalizergraphics.com/documents/ParallelRenderingSystems.pdf}
  {http://www.equalizergraphics.com/documents/ParallelRenderingSystems.pdf}}\\
\end{tabularx}}
\clearpage
\pagenumbering{arabic}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\columnwidth]{images/sp_to_mp.pdf}
\caption{Some advanced display systems}
\label{FIG_multipipe}
\end{figure}
